### 2017-04-13 paper/oopsla17-submission/intro2.tex
asd

% In Robin Milner's memorable words
% %
% ``types are the leaven of computer programming;
  % they make it digestible''~\cite{tapl}.
%
Types are wonderful.
%
Languages like \ocaml and \haskell make
the value-proposition for types even more
appealing by using constraints to automatically
synthesize the types for all program terms
without troubling the programmer for any
annotations.
%
Unfortunately, this automation has come at a price.
Verbose type annotations (as in, \eg, Java) signify
the programmer's intent and help to correctly
blame the erroneous sub-term when the code is
ill-typed.
%
In contrast, lacking such signifiers, automatic
type inference algorithms are prone to report
type errors quite far from their actual source.
%
While this can seem like a minor annoyance to
veteran programmers, it turns out to be a significant
stumbling block for novices~\citep{Wand1986-nw,Joosten1993-yx}.

@@

\mypara{A Data-Driven Approach}
%
In this paper, we introduce \toolname \footnote{Numeric Analysis of Type Errors}
a \emph{data-driven} approach to error
localization based on supervised
classification~\citep{Kotsiantis2007-pj}.
%
\toolname works by using a large corpus
of training data --- pairs of ill-typed
programs and their ``fixed'' versions ---
to automatically \emph{learn a model}
of where the error is most likely.
%
When given a new ill-typed program,
\toolname simply executes the model
to generate a list of likely error
locations ranked by likelihood.
%
We evaluate \toolname by comparing its
precision against the state-of-the-art
on a set of over 4,500 ill-typed Ocaml
programs drawn from introductory
programming classes.
%
We show that \toolname's data-driven
model is able to correctly predict
the exact sub-expression that needs to
be changed, 74\% of the time compared
to \ocaml's 45\% and \sherrloc's 56\%.
%
When the \emph{top} ranked location
is considered. \toolname's accuracy jumps
to above 85\% (resp. 90\%) when we consider
the \emph{top-2} and \emph{top-3} locations.
%
We achieve these advances by identifying
and then solving three key challenges.

>>>>

% In Robin Milner's memorable words
% %
% ``types are the leaven of computer programming;
  % they make it digestible''~\cite{tapl}.
%
Types are awesome.
%
Languages like \ocaml and \haskell make
the value-proposition for types even more
appealing by using constraints to automatically
synthesize the types for all program terms
without troubling the programmer for any
annotations.
%
Unfortunately, this automation has come at a price.
Verbose type annotations (as in, \eg, Java) signify
the programmer's intent and help to correctly
blame the erroneous sub-term when the code is
ill-typed.
%
In contrast, lacking such signifiers, automatic
type inference algorithms are prone to report
type errors quite far from their actual source.
%
While this can seem like a minor annoyance to
veteran programmers, it turns out to be a significant
stumbling block for novices~\citep{Wand1986-nw,Joosten1993-yx}.

@@

\mypara{A Data-Driven Approach}
%
In this paper, we introduce \toolname
\footnote{``Numeric Analysis of Type Errors''; any resemblance to persons living or dead is purely coincidental.}
a \emph{data-driven} approach to error
localization based on supervised
classification~\citep{Kotsiantis2007-pj}.
%
\toolname works by using a large corpus
of training data --- pairs of ill-typed
programs and their fixed versions ---
to automatically \emph{learn a model}
of where the error is most likely.
%
When given a new ill-typed program,
\toolname simply executes the model
to generate a list of likely error
locations ranked by likelihood.
%
We evaluate \toolname by comparing its
precision against the state-of-the-art
on a set of over 4,500 ill-typed Ocaml
programs drawn from introductory
programming classes.
%
We show that \toolname's data-driven
model is able to correctly predict
the exact sub-expression that needs to
be changed, 74\% of the time, which is
29 points higher than \ocaml, and
18 points higher than the state-of-the-art
\sherrloc tool.
%
Further, \toolname's accuracy surpasses
85\% when we consider the \emph{top-2}
locations and reaches 91\% if consider
the \emph{top-3}.
%
We achieve these advances by identifying
and then solving three key challenges.
